An efficient acyclic contact planner for multiped robots

### 2017-01-13 body/conclusion.tex
conclusion

In the example of \cite{Bouyarmane2009}, the verification of \equilibriumfeasibility implies a constructive demonstration by exhibiting a valid $\mathbf{q}^{\overline{0}}$, requiring
several minutes of planning. Our method, in comparison, takes from a few milliseconds to several seconds.

@@

\begin{figure}[t]
\centering
  \begin{overpic}[width=1\linewidth]{figures/2D_feas}
		\put (15,) {$C_{Equil}^0$      $\subset$} 
		\put (47,) {$C_{Contact}^0$ $\approx$ } 
		\put (76,) {$C_{Reach}^0$} 
	\end{overpic}
\caption{Illustration of several root configurations sets used in this paper in a 2D scene. Obstacles are violet, and units are in meters. To show the sets in a 2D representation, all the rotational joints of HRP-2 are locked in the shown configuration, such that a torso configuration
is only described by two positional parameters (x and y). The root of the robot is indicated with a black cross. To compute the reachable workspace, the point on the ankle indicated by a green cross was used. $C_{Equil}^0$ is included in $C_{Contact}^0$. $C_{Reach}^0$ approximates $C_{Contact}^0$. Depending on a parametrization, we can obtain $C_{Contact}^0 \subset C_{Reach}^0$. Considering the configurations around the top obstacle, we can observe a dramatic
divergence between  $C_{Equil}^0$  and $C_{Contact}^0$ when the problem is not \textit{\gls{cluttered}}.}
		   \label{fig:dedefeas}
\end{figure}

@@

In this paper we consider the \gls{cluttered} contact planning problem, formulated as two sub-problems that we address sequentially.
The first problem $\mathcal{P}_1$ consists in computing an \gls{equilibrium feasible} guide path for the root of the robot;
 the second problem $\mathcal{P}_2$ is the computation of a discrete sequence of whole-body configurations along the root path.

Our contribution to \Pa is the introduction of a low-dimensional space $C_{reach}$, an approximation of the space of \gls{equilibrium feasible} root configurations.
Thanks to the computationally efficient verification of the \gls{reachc}, we are able to solve \Pa much faster than previous approaches.

@@

Our results demonstrate that our method allows a pragmatic compromise between three 
criteria that are hard to conciliate: generality, performance, and quality of the solution, making it the first acyclic contact
planner compatible with \gls{interactive} applications.
%
\textbf{Regarding generality}, the \gls{reachc}, coupled with an approach based on limb decomposition, 
allows the method to address arbitrary multiped robots in \gls{cluttered} problems. The only pre-requisite is the specification 
of the volumes $W^0$.
%
\textbf{Regarding performance}, our framework is really efficient in addressing both \Pa and $\mathcal{P}_2$. This results in \gls{interactive} computation times.
%
\textbf{Regarding the quality of the paths}, the \gls{reachc} allows us to compute
\gls{equilibrium feasible} paths in all the presented scenarios, with low rejection rates.
As for \cite{Bouyarmane2009}, failures can still occur, due to the approximate condition used to compute the guide path.
The low computational burden of our framework however allows for fast re-planning in case of failure.
Furthermore because of this approximation, the guide search is not complete. The choice is deliberate, because we are convinced
that it is necessary to trade completeness for efficiency at all stages of the planner.
However, one direction for future work is to focus on a more accurate formulation of $C_{reach}^0$ to improve
the approximation.

Another limitation of the method is that it currently only applies to \gls{cluttered} problems.
However, it should first be noted that many problems belong to this class: for instance all the problems
at the DRC were \gls{cluttered}. Our method is thus already useful for many cases.
One way of extending its range of application, that we 
consider for future work, is to include the equilibrium criterion when solving $\mathcal{P}_1$.
Considering the set of obstacles intersecting with the reachable workspace for a given root configuration as candidates surfaces, we can use them to verify the equilibrium criterion.
This would give us a necessary condition for \equilibriumfeasibility.

Regarding the interpolation between the contact sequences ($\mathcal{P}_3$), we have already obtained some success for some of the computed sequences~\citep{Carpentier2016}, but additional
work is required on the planning side to obtain a seamless workflow. To achieve this, we are currently working on the notion of transition certificate, i.e. formulating
conditions that guarantee that the interpolation between two contact configurations is dynamically feasible.
%~ Our current direction is to propose a geometric quantification of both the kinematic and dynamic constraints of the problem, expressed
%~ at the center of mass of the robot.
 %~ We are also
%~ working on new heuristics more closely related to the dynamics of the systems (for instance, choose the contacts that minimize the jerk between two contact configurations).
A last limitation of our method is that only static equilibrium configurations are considered for contact planning.
We aim at performing kinodynamic planning to overcome this limitation. We believe that the most promising direction in this regard is to integrate
the notion of Admissible Velocity Propagation in our current work \citep{DBLP:conf/rss/PhamCN13}.
Addressing these two last issues is essential to bridge the gap between the planning and control aspects of multiped locomotion.

>>>>

In the example of \cite{Bouyarmane2009}, the verification of \equilibriumfeasibility\ implies a constructive demonstration by exhibiting a valid $\mathbf{q}^{\overline{0}}$, requiring
several minutes of planning. Our method, in comparison, takes from a few milliseconds to several seconds.

@@

\begin{figure}[t]
\centering
  \begin{overpic}[width=1\linewidth]{figures/2D_feas}
		\put (15,) {$C_{Equil}^0$      $\subset$} 
		\put (47,) {$C_{Contact}^0$ $\approx$ } 
		\put (76,) {$C_{Reach}^0$} 
	\end{overpic}
\caption{Illustration of several root configurations sets used in this paper in a 2D scene. Obstacles are violet, and units are in meters. To show the sets in a 2D representation, all the rotational joints of HRP-2 are locked in the shown configuration, such that a torso configuration
is only described by two positional parameters (x and y). The root of the robot is indicated with a black cross. To compute the reachable workspace, the point on the ankle indicated by a green cross was used. $C_{Equil}^0$ is included in $C_{Contact}^0$. $C_{Reach}^0$ approximates $C_{Contact}^0$. Depending on a parametrization, we can obtain $C_{Contact}^0 \subset C_{Reach}^0$. Considering the configurations around the top obstacle, we can observe a similarity between  $C_{Equil}^0$  and $C_{Contact}^0$ when the reachable workspace of the legs includes \textit{quasi-flat} surfaces.}
		   \label{fig:dedefeas}
\end{figure}

@@

In this paper we consider the multi contact planning problem, formulated as two sub-problems that we address sequentially.
The first problem $\mathcal{P}_1$ consists in computing an \gls{equilibrium feasible} guide path for the root of the robot;
 the second problem $\mathcal{P}_2$ is the computation of a discrete sequence of whole-body configurations along the root path.

Our contribution to \Pa is the introduction of a low-dimensional space $C_{reach}^0$, an approximation of the space of \gls{equilibrium feasible} root configurations.
$C_{reach}^0$ can be efficiently sampled and has a low-dimension. For these reasons we are able to solve \Pa much faster than previous approaches.

@@

Our results demonstrate that our method allows a pragmatic compromise between three 
criteria that are hard to conciliate: generality, performance, and quality of the solution, making it the first acyclic contact
planner compatible with \gls{interactive} applications.
%
\textbf{Regarding generality}, the \textit{reachability condition}, coupled with an approach based on limb decomposition, 
allows the method to address automatically arbitrary multiped robots.
%
\textbf{Regarding performance}, our framework is really efficient in addressing both \Pa and $\mathcal{P}_2$. This results in \gls{interactive} computation times.
%
\textbf{Regarding the quality of the paths}, we are able to compute
\gls{equilibrium feasible} paths in all the presented scenarios, with a high success rates.
As for \cite{Bouyarmane2009}, failures can still occur, due to the approximate condition used to compute the guide path.
The low computational burden of our framework however allows for fast re-planning in case of failure.
Furthermore because of this approximation, the guide search is not complete. The choice is deliberate, because we are convinced
that it is necessary to trade completeness for efficiency at all stages of the planner.
However, one direction for future work is to focus on a more accurate formulation of $C_{reach}^0$ to improve
the approximation.

Our method applies to any \textit{quasi-flat} scenario, where at least one contact friction cone contains
the direction opposed to the gravity. This class of scenarios include all the problems proposed at the DARPA Robotics challenge.
One way of further extending its range of application, that we consider for future work, is to include the equilibrium criterion when solving $\mathcal{P}_1$.
Considering the set of obstacles intersecting with the reachable workspace for a given root configuration as candidates surfaces, we can use them to verify the equilibrium criterion.
This would give us a necessary condition for \equilibriumfeasibility.

While we have exhibited complete multi contact locomotion obtained with our contact planner, our main concern for future work is to address the interpolation
between contact sequences ($\mathcal{P}_3$), not addressed in this work, which remains an open issue in really constrained scenarios.
Adressing $\mathcal{P}_3$ requires addressing efficiently the collision avoidance problem during the interpolation,	but also improving
our plans with transition certificates, i.e. guarantees that the interpolation between two contact configurations is feasible.
%~ Our current direction is to propose a geometric quantification of both the kinematic and dynamic constraints of the problem, expressed
%~ at the center of mass of the robot.
 %~ We are also
%~ working on new heuristics more closely related to the dynamics of the systems (for instance, choose the contacts that minimize the jerk between two contact configurations).
Finally, we aim at performing kinodynamic planning to remove the constraint that configurations in the contact plan should be in static equilibrium. We believe that the most promising direction in this regard is to integrate the notion of Admissible Velocity Propagation in our current work \citep{DBLP:conf/rss/PhamCN13}.
Addressing these two issues is essential to bridge the gap between the planning and control aspects of multiped locomotion.
